An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-11 paper.tex
Added more gait database citations.
Fixes #126.

\cite{Chester2007} report on a large gait database comparison where one
database contained kinematic data of 409 gait cycles of children from 1 to 7
years old but the data does not seem to be publicly available. This is,
unfortunately, typical. \cite{Tirosh2010} recognized the need for a
comprehensive data base for clinical gait data and created the Gaitabase. This
database may contain a substantial amount of data but it is encumbered by a
complicated and restrictive license and sharing scheme. However, there are
examples of data with less restrictions. The University of Wisconsin at
LaCrosse has an easily accessible normative gait data set \citep{Willson2014}
from 25 subjects with lower extremity marker data from multiple gait cycles and
force plate measurements from a single gait cycle.

More recent examples of biomechanists sharing their data alongside publications
are: \cite{Bogert2013} which includes full body joint kinematics and kinetics
from eleven subjects walking on an instrumented treadmill and \cite{Wang2014}
who includes a larger set of data from ten subjects walking for five minutes
each at three different speeds but only a small set of lower extremity markers
are present. The second is notable because it publishes the data in Dryad, a
modern citable data repository.

>>>>

\cite{Chester2007} report on a large gait database comparison where one
database contained kinematic data of 409 gait cycles of children from 1 to 7
years old but the data does not seem to be publicly available. This is,
unfortunately, typical. \cite{Tirosh2010} recognized the need for a
comprehensive data base for clinical gait data and created the Gaitabase. This
database may contain a substantial amount of data but it is encumbered by a
complicated and restrictive license and sharing scheme. \cite{Yun2014} provides
lower body kinematic data of single gait cycles from over one hundred subjects
extracted from the large KIST Human Gait Pattern Data database which may also
include a substantial amount of raw data but it is private. However, there are
examples of data with less restrictions. The University of Wisconsin at
LaCrosse has an easily accessible normative gait data set \citep{Willson2014}
from 25 subjects with lower extremity marker data from multiple gait cycles and
force plate measurements from a single gait cycle. The CMU Graphics Lab
Motion Capture Database~\citep{CMU2015} is also a good example and contains
full body marker kinematics for a fair number of trials with small number of
gait cycles during both walking and running.

More recent examples of biomechanists sharing their data alongside publications
are: \cite{Bogert2013} which includes full body joint kinematics and kinetics
from eleven subjects walking on an instrumented treadmill and \cite{Wang2014}
who includes a larger set of data from ten subjects walking for five minutes
each at three different speeds but only a small set of lower extremity markers
are present. The second is notable because it publishes the data in Dryad, a
modern citable data repository. It is also worth noting purely visual data
collections of gait, like the one presented in \cite{Makihara2012}, which
contain videos of subjects walking on a treadmill in full clothing. This
database is also unfortunately tightly secured with an extensive release
agreement for reuse.
